User manual for \texttt{casl\_p4est}

### 2016-04-05 doc/casl_p4est_manual/casl_p4est_manual.tex
updating manual

>>>>

Most of the communication can be handled with the \ttt{Vec} data type provided by Petsc. The \ttt{Petsc} library is thoroughly documented online. A \ttt{Vec} is an array that can have a ghost chunk. A ghosted array can be created with the data located at the quadrants' center or at the nodes. The nodes code is
\begin{Verbatim}[frame=single]
Vec phi;
VecCreateGhostNodes(p4est, nodes, &phi);
\end{Verbatim}
The actual data stored in the \ttt{Vec} can be accessed by
\begin{Verbatim}[frame=single]
double *phi;
VecGetArray(phi, &phi_p);
for (p4est_locidx_t n = 0; n<nodes->num_owned_indeps; ++n)
{
  (do something with phi_p)
}
VecRestoreArray(phi, &phi_p);
\end{Verbatim}
In the previous code, the pointer \ttt{phi\_p} points to a contiguous array of the local part of the data stored in the \ttt{Vec}. \ttt{Petsc} does not guarantee that the local part and the ghosted part are stored in the same location, and therefore accessing the entire data - including the ghosted part - should be done after getting the local form of the \ttt{Vec}
\begin{Verbatim}[frame=single]
Vec phi_loc;
double *phi_p;
VecGhostGetLocalForm(phi, &phi_loc);
VecGetArray(phi_loc, &phi_p);
for(size_t n=0; n<nodes->indep_nodes.elem_count; ++n)
{
  (do something with phi_p)
}
VecRestoreArray(phi_loc, &phi_p);
VecGhostRestoreLocalForm(phi, &phi_loc);
\end{Verbatim}
In many places in the library, the ghosted values are accessed without first accessing the local form of the \ttt{Vec}, this is a dangerous practice that has worked ... so far.

The ghost values can be synchronized with the remote processes through the \ttt{Petsc} API, thus leading to the general communication layout
\begin{Verbatim}[frame=single]
{ do work for local values shared with other processes }
VecGhostUpdateBegin(phi, INSERT_VALUES, SCATTER_FORWARD);
{ do work for local values not shared with other processes }
VecGhostUpdateEnd(phi, INSERT_VALUES, SCATTER_FORWARD);
\end{Verbatim}
